Differential Expression - HBCC - dsACC - Dx

### 2020-07-31 individual-cohorts/HBCC_dsACC_DE.Rmd

L = cbind(L1, L2, L3)

contrast <- c(glue::glue_collapse(names(L1[L1 != 0]), "-"), 
              glue::glue_collapse(names(L2[L2 != 0]), "-"),
              glue::glue_collapse(names(L3[L3 != 0]), "-")
)

>>>>

# Manually set comparison of SCZ-Other to Control
L = cbind(L1, L2, L3, data.frame(L4 = c(1, -0.5, -0.5, 0, 0, 0, 0, 0)))
contrast <- c(glue::glue_collapse(names(L1[L1 != 0]), "-"), 
              glue::glue_collapse(names(L2[L2 != 0]), "-"),
              glue::glue_collapse(names(L3[L3 != 0]), "-"),
              glue::glue("DxControl-DxOtherDxSCZ")
)
